### 2016-06-30 ch02-qlogms/excitation-design.tex
Ch02: figure + clarification variance reduction

\section{Input Design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ is a rational, time invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.

@@

Typically, the input design formulation depends on the true system parameters. This means that the optimal input depends on the \emph{unknown} system that one wants to identify. 
Furthermore, classical input designs, such as the D-optimal design, typically give signals with sparse spectra. 
This means that only a few frequencies are excited. 
A sparse spectrum is bad from a robustness point of view; there is very limited information about what happens at the unexcited frequencies. 
Therefore, a signal design to be optimal for one system may result in very bad estimates if applied to another system.
To increase the robustness of the design, one could take a small fraction $\delta$, from the optimal power and redistribute this power over the whole frequency band of interest.
From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the input power by $1-\delta$, gives the transfer function variance
\begin{align}
\var{\hat{G}(j\omega)}\frac{1}{1-\delta}.
\end{align}
This is a small loss while the increase in robustness can be significant if the added signal is robust. Such a robust signal is studied in the following parts of the chapter.

>>>>

\section{Input Design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ is a rational, time-invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.

@@

Typically, the input design formulation depends on the true system parameters. This means that the optimal input depends on the \emph{unknown} system that one wants to identify. 
Furthermore, classical input designs, such as the D-optimal design, typically give signals with sparse spectra. 
This means that only a few frequencies are excited. 
A sparse spectrum is bad from a robustness point of view; there is very limited information about what happens at the unexcited frequencies. 
Therefore, a signal design to be optimal for one system may result in very bad estimates if applied to another system.
To increase the robustness of the design, one could take a small fraction $\delta$, from the optimal power and redistribute this power over the whole frequency band of interest.
From \eqref{eq:excitation:IF} and \eqref{eq:excitation:varG} we see that scaling the optimal input power by $1-\delta$, has the following effect on the variance of the estimate:
\begin{align}
\var{\hat{G}(j\omega)}_{{(1-\delta)\mathrm{optimal} + \delta \mathrm{robust}}} \approx \frac{1}{1-\delta} \var{\hat{G}(j\omega)}_{\mathrm{optimal}} 
\text{.}
\end{align}
This is a small loss while the increase in robustness can be significant if the added signal is robust. 
Such a robust signal is studied in the following parts of the chapter.
